Reassessing the Impact of Dynamic Slicing in SFL

### 2019-01-06 paper/ijcai/paper.tex
stats added

@@

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (kLOC) & \# Tests & \# Defects \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.}
\end{table}
\normalsize

@@

\subsection{Experiments}

These experiments only consider 213 of 395 bugs of the \dfj. 
Each bug has one or more failing tests associated. For each test, it is verified if all the faulty statements of the bug are in the slicer. \#Ev is the total number of verifications performed by bug. For each bug ($i$) of the project, this experiment checks if all the faulty statements of the bug ($FS_i$) are in the slicer retrieved by each test ($T_i$). $n$ is the total number of bugs considered for each project.

$$\#Ev = \sum_{i=1}^{n} T_i * FS_i$$

\Sof{It does not make much sense to report \#Bugs here. If we end up not using the all dataset I think it would be better to report this in another section.}
To evaluate the performance of \ds{} alone, the following metrics were taken into consideration: the total number of faulty statements ($\#FS$) in each project; the total number of tests ($\#T$) in each project; the number of times that each $FS$ may be in the slicer of each $T$, $\#Ev$; the number of bugs considered per project to the experiments, $\#Bugs$; the percentage of $FS$ that are not in the slicers of $T$, \% $\overline{in}$; the percentage of $FS$ that are not found in the top-5 of the classes with the highest ranks of suspiciousness; and, the percentage of $FS$ that are in the slicers of $T$. Regarding the \sfl{}+\ds{} combination, performance is evaluated based on four different metrics: the probability of the first line being the faulty one, $\% imp(f)$; the probability of the last line being the faulty one, $\% imp(l)$; and, finally the mean, $\% imp(\overline{m})$, and median $\% imp (median)$ of the position of the faulty line in the ranking. This combination is evaluated considering all the classes of the project (all) and only the classes of the project involved in the failing tests execution (loaded).

@@

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lccccccc}
		\toprule
		Project            &  \% top-5 & \%  $\overline{in}$  & \% in  \\ % & \#FS  & \# T & \# Ev & \#Bugs
		\midrule
		\chart{} 	& 0\% & 13.2\% & 86.8\%   \\ %& 40 &  57  &  136 & 21 
		\closure{} 	& 3.7\% & 0\% & 96.3\%   \\ %& 56 &  10  &  81 & 6 
		\lang{} 	& 0\% & 0\%  & 100\%   \\ % & 204 &  90  &  447 & 59 
		\cmath{} 	& 2.1\% & 8\% & 89.9\%   \\ % & 299 &  112  &  438 & 86 
		\mockito{} 	& 3.5\% & 3.3\% & 93.2\%   \\ % & 94 &  93  &  397 & 25 
		\jtime{} 	& 0\% & 1.2\% & 98.8\%   \\ % & 63 &  49  &  171 & 16 
		\bottomrule
				%Total 	& 756 &  411  &  1670 & 213 &  &  &   \\
	\end{tabular}
	\caption {Report of the capability of \ds{} on missing faulty statements}
\end{table*}
\normalsize

\subsubsection{\textit{How effective is the \sfl{}+\ds{} combination for bug localization?}}

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{2pt}
	\begin{tabular}{lcccccccc}
		\toprule

			    \multirow{2}{*}{Project}   & \multicolumn{4}{c}{all} & \multicolumn{4}{c}{loaded}  \\

		             & \% imp (f) &\% imp (l) & \% imp ($\overline{m}$)& \% imp (median) &\% imp (f) & \% imp (l)   & \% imp ($\overline{m}$) & \% imp (median)  \\ %\comments{& Failing Test Cases &}  
		\midrule

		\chart{}  & 20.98\% & 20.32\% & 20.05\% & 19.75\% & 20.98\% & 20.32\% & 20.05\% & 19.75\% \\
		\closure{}         & 4.17\% & 0.00\% & 0.00\% & 3.68\% & 4.17\% & 0.00\% & 0.00\% & 3.68\% \\
		\lang{}             &7.91\% & 5.84\% & 6.47\% & 6.80\% & 7.91\% & 5.84\% & 6.47\% & 6.80\% \\
		\cmath{}           &8.58\% & 6.59\% & 7.65\% & 8.74\% & 8.58\% & 6.59\% & 7.65\% & 8.74\% \\
		\mockito{} & 15.73\% & 17.37\% & 17.63\% & 15.74\% & 15.73\% & 17.37\% & 17.63\% & 15.74\% \\
		\jtime{}           & 8.83\% & 10.70\% & 11.25\% & 10.86\% & 8.83\% & 10.70\% & 11.25\% & 10.86\% \\
		\bottomrule
	\end{tabular}
	\caption {\sfl{}+\ds{} performance evaluation}
\end{table*}
\normalsize

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	  \begin{tabular}{lrrr}
		\toprule
		Project            & top-5 & top-10 & imp   \\ %\comments{& Failing Test Cases &}
		\midrule
		\lang{}            & 55 & 55 & 0 \%       \\   %\commentst{& 124   &  -}\\
		\cmath{}           & 87  & 91 & 3.77 \%     \\   %\comments{& 177   &  -}\\
		\closure{}         & 83  & 96  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 22  & 24 & 7.69 \%      \\  %\comments{& 92    &  -}\\
		\jtime{}           & 21  & 27 & 3.70 \%       \\   %\comments{& 76    &  -}\\
		\mockito{}         & 24  & 27 & 7.89 \%    \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Diagnosis Capability without Slicing}
  \end{table}
  \normalsize

@@

@@

\subsubsection{Applications}

Ishii and Kutsuna ~\cite{li-huo-chen-zhong-feng-li-2013} proposed a
technique involving dynamic slicing and SFL applied to MATLAB/Simulink
models. The technique consists of iteratively
generating tests that cause an error using satisfiability modulo
theories (SMT) so that the slices generated are distinct from each
other.  For slicing, their technique uses a program dependence graph
(PDG) that express both data and control dependencies between blocks,
so that the slice is built only on blocks that affect a specific line
in the model - \textit{effective blocks}.  Their goal with the slicing
was (1) to keep suspiciousness of a fault maximum if a target model
has only one fault, and (2), to reduce the number of fault candidates
obtained by the slicer.  For this, they utilize only failed test cases
generated with SMT solvers ~\cite{peleska-vorobev-lapschies-2011} to
calculate suspiciousness, as passed test cases might lower the
suspiciousness of a fault.  The calculated suspiciousness is the
number of times that a block belongs to the \textit{effective blocks}
group by the number of total failed test cases.  Although their
experiments and results showed promise with small models, the accuracy
of the technique decreases when applied to models with multiple faults
instead of one, as does the efficiency when exposed to large models,
number of generated tests, sizes of sliced models and so on.

\subsubsection{Automatic Program Repair}
Automated repair techiniques have received considerable attention on
the last decade and consists of three basic steps: fault localization, patch
generation, and patch validation.  Regarding the fault localization
step, Automated Program Repair (APR) tools can be guided by statistical
fault localization techiniques to modify code which most likely
contains the fault. On this section, we will briefly describe some of
these tools.
\Davino { Not necessarily on the paper and not necessarily on a related work section. To be revised/moved/sliced later. }

GenProg\Fix{cite} is a state of the art tool based on genetic
programming to repair defects in off-the-shelf C programs. GenProg's
strategy to fault localization consists of instrumenting the program
so that all lines visited when executing failing test cases are
recorded and used on the genetic search algorithm. The algorithm
involves serching for other parts of the program, considering that a
program that contains an error in one area likely implements the
correct behaviour elsewhere. The tool proved to be effective in
reparing 16 programs involving 1.25 millions LOC, and efficient as the
algorithm search space takes advantage of test case coverage
information, reusing  existing program statements.

Debroy and Wong\Fix{cite} presented a techinique for automatically
fixing faults in a program combining both mutation and statistical
fault localization. Using the Tarantula fault localizer\Fix{cite}, the
techinique focus the top ranked statements in terms of suspiciousness
for the mutation operations. The percentage of statements examined in
search for the fault is based on the total number of statements of the
program, with the 10 percent being a reasonable number on the subject
programs studied.

JAFF\Fix{cite} is a Java automatic repair tool based on evolutionary principles that uses fault localization for ranking the statements in the code in terms of suspiciousness level.
Before searching for the fix, the Java program is translated into a syntax tree composed of nodes related to the top ranked statements being used on the search process.
The tool uses a specific formula to get the number of nodes that will be used on the search based on the number of statements with the same rank of suspiciousness,
with the range between 1 to 20 nodes being used on the cases studied.

SemFix is based on symbolic execution, constraint solving and program synthesis applied to software automatic repair. The tool uses statistical fault localization (SFL) with Tarantula to
obtain the rank of suspiciousness and iteratively takes the most suspicious statement that has not been tried out to be used on the search for a fix. Compared to GenProg, the presented tool
took consideredably less time to find a fix for programs utilizing the same test suites. However, the authors mention that the choice of the SFL techinique could potentially affect the
effectiviness of the tool, particularly with large programs.

SPR\Fix{cite} \Davino{ Fan Long } is based on staged
program repair with condition synthesis. SPR uses fault localization
to identify target statements that will be transformed in search for a
fix on the program. The search space is built with a list of
statements ranked by suspiciousness level, where only the first 200
ranked statements are considered. The authors observed that increasing
the search space to the top 2000 statements would bring additional
repairs, but with a obvious cost of searching a large space.
\Davino { Another tool presented by the same authors is Prophet, which uses the same search space, top 200. }

MintHint \Fix{cite} uses statistical analysis with SFL to rank
statements by their likelihood of being faulty. Given the ranked list,
the tool analysis the top \textit{k} statements, where \textit{k} is a
threshold set by the user, and proceeds with the repair algorithm
assuming the fault can be repaired by changing a single statement.

\Davino { Another set of automatic program repair tools that doesn't use fault localization includes: CodePhage, ClearView, PAR, RSRepair, Kali, and AutoFix, among others. }

\section{Conclusions and Future Work}\label{sec:conc}
\section*{Acknowledgments}

@@

>>>>

To evaluate the performance of the \comb{} combination
suggested to improve \sfl{}

@@

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (kLOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.}
\end{table}
\normalsize

@@

\subsection{Methodology}

Aiming the evaluation of the \comb{} performance, three main 
experiements were performed: only using \sfl{} top calculate the statements
rank, . First, for each version

@@

\begin{table*}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{llllll}
		\toprule
		Project             &  \# MFS-5  & \% MFS-5 & \# MFS-10 & \% MFS-10 & \# Faults \\ % & \#FS  & \# T & \# Ev & \#Bugs
		\midrule
		\chart{}  & 6 & 23.1\% & 4 & 15.4 \%  & 26\\ %& 40 &  57  &  136 & 21 
		% \closure{} 	& 3.7\% & 0\% & 96.3\%   \\ %& 56 &  10  &  81 & 6 
		% \lang{} 	& 0\% & 0\%  & 100\%   \\ % & 204 &  90  &  447 & 59 
		% \cmath{} 	& 2.1\% & 8\% & 89.9\%   \\ % & 299 &  112  &  438 & 86 
		% \mockito{} 	& 3.5\% & 3.3\% & 93.2\%   \\ % & 94 &  93  &  397 & 25 
		% \jtime{} 	& 0\% & 1.2\% & 98.8\%   \\ % & 63 &  49  &  171 & 16 
		\bottomrule
				%Total 	& 756 &  411  &  1670 & 213 &  &  &   \\
	\end{tabular}
	\caption {Report of the capability of \ds{} on missing faulty statements}
\end{table*}
\normalsize

\subsubsection{\textit{How effective is the \comb{} combination for bug localization?}}

The \comb{} combination yields an average improvement of, approximately, 19\% on the ranking of the faulty statements of the \chart{}
project. Figure \ref{table:performance}, reports the average rank of all faulty statements for each version of \chart{} project after
applying two main techiniques (\sfl{} and \comb{})

% \begin{table*}[h]
% 	\centering
% 	\setlength{\tabcolsep}{2pt}
% 	\begin{tabular}{lcccccccc}
% 		\toprule

% 			    \multirow{2}{*}{Project}   & \multicolumn{4}{c}{all} & \multicolumn{4}{c}{loaded}  \\

% 		             & \% imp (f) &\% imp (l) & \% imp ($\overline{m}$)& \% imp (median) &\% imp (f) & \% imp (l)   & \% imp ($\overline{m}$) & \% imp (median)  \\ %\comments{& Failing Test Cases &}  
% 		\midrule

% 		\chart{}  & 20.98\% & 20.32\% & 20.05\% & 19.75\% & 20.98\% & 20.32\% & 20.05\% & 19.75\% \\
% 		\closure{}         & 4.17\% & 0.00\% & 0.00\% & 3.68\% & 4.17\% & 0.00\% & 0.00\% & 3.68\% \\
% 		\lang{}             &7.91\% & 5.84\% & 6.47\% & 6.80\% & 7.91\% & 5.84\% & 6.47\% & 6.80\% \\
% 		\cmath{}           &8.58\% & 6.59\% & 7.65\% & 8.74\% & 8.58\% & 6.59\% & 7.65\% & 8.74\% \\
% 		\mockito{} & 15.73\% & 17.37\% & 17.63\% & 15.74\% & 15.73\% & 17.37\% & 17.63\% & 15.74\% \\
% 		\jtime{}           & 8.83\% & 10.70\% & 11.25\% & 10.86\% & 8.83\% & 10.70\% & 11.25\% & 10.86\% \\
% 		\bottomrule
% 	\end{tabular}
% 	\caption {\sfl{}+\ds{} performance evaluation}
% \end{table*}
% \normalsize

% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{table*}[h]
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{llllllllllllll}
		\toprule
		   & 1       & 2       & 3       & 4       & 5       & 6       & 7       & 8       & 9       & 10      & 11      & 12      & 13      \\\midrule
	red-5  & 81.46\% & 79.06\% & 80.10\% & 0.00\%  & 50.35\% & 86.30\% & 78.71\% & 78.73\% & 44.47\% & 84.29\% & 82.94\% & 38.90\% & 58.46\% \\
	red-10 & 16.71\% & 75.96\% & 35.93\% & 12.16\% & 50.35\% & 86.30\% & 81.02\% & 78.73\% & 54.69\% & 84.29\% & 82.94\% & 20.88\% & 61.85\% \\\midrule
		   & 14      & 15      & 16      & 17      & 18      & 19      & 20      & 21      & 22      & 23      & 24      & 25      & 26      \\\midrule
	red-5  & 66.23\% & 66.00\% & 51.13\% & 49.24\% & 71.76\% & 69.81\% & 82.82\% & 74.84\% & 46.60\% & 22.11\% & 18.39\% & 78.99\% & 0.00\%  \\
	red-10 & 67.43\% & 69.98\% & 47.11\% & 55.59\% & 72.84\% & 68.40\% & 68.85\% & 54.43\% & 46.60\% & 37.50\% & 18.39\% & 45.68\% & 0.00\%  \\
		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction performance for each version of the \chart{} project considering only the top-5 and top-10 classes}
	\label{table:reduction}
\end{table*}

\begin{table*}[h]
	\setlength{\tabcolsep}{3pt}
	\begin{tabular}{@{}p{1.75cm}p{0.8cm}p{1.6cm}p{1.3cm}p{0.8cm}p{1.2cm}p{0.8cm}p{0.8cm}p{0.8cm}p{1.5cm}p{1cm}p{0.8cm}p{1.3cm}p{0.8cm}@{}}
	\toprule
		   & 1    & 2   & 3  & 4   & 5           & 6   & 7  & 8    & 9            & 10     & 11 & 12      & 13   \\ \midrule
	SFL    & 36   & 265.5625    & 6.5         & 173 & 7.5         & 57  & 72 & 9.5  & 8.5          & 2.5    & 10 & 19.5    & 44.5 \\
	\comb{}-5   & 15.5 & 716.5       & 5           & 107 & 7           & 15  & 44 & 8    & 8.5          & 2      & 6  & 2410    & 35.5 \\
	\comb{}-10  & 35.5 & 406.375     & 5           & 114 & 7           & 15  & 46 & 8    & 8.5          & 2      & 6  & 2448    & 35.5 \\
	\cellcolor[HTML]{FFFFC7}IMP-5  & 20.5 & -450.9375   & 1.5         & 66  & 0.5         & 42  & 28 & 1.5  & 0            & 0.5    & 4  & -2390.5 & 9    \\
	\cellcolor[HTML]{FFFFC7}IMP-10 & 0.5  & -140.8125   & 1.5         & 59  & 0.5         & 42  & 26 & 1.5  & 0            & 0.5    & 4  & -2428.5 & 9    \\
	\cellcolor[HTML]{9AFF99}IMP    & {\success20.5} & X  & {\success1.5} & {\success66}  & {\success0.5} & {\success42}  & {\success28} & {\success1.5}  & 0 & {\success0.5} & {\success4}  & X & {\success9}    \\\midrule
		   & 14   & 15          & 16          & 17  & 18          & 19  & 20 & 21   & 22           & 23     & 24 & 25      & 26   \\\midrule
	SFL    & 15.5 & 2471.1667 & 13.5        & 2   & 9.5         & 3.5 & 6  & 39   & 57.2143  & 6818.5 & 3  & 3516    & 140  \\
	\comb{}-5   & 15.5 & 2254.1667 & 9.1667 & 2   & 7.6667 & 2.5 & 6  & 21   & 105.4286  & 6818.5 & 3  & 6046.5  & 717  \\
	\comb{}-10  & 15.5 & 2264.8333 & 10.8333 & 2   & 7.6667 & 2.5 & 6  & 29.5 & 105.4286  & 6818.5 & 3  & 6063.5  & 140  \\
	\cellcolor[HTML]{FFFFC7}IMP-5  & 0    & 217         & 4.3333 & 0   & 1.8333 & 1   & 0  & 18   & -48.2143 & 0      & 0  & -2530.5 & -577 \\
	\cellcolor[HTML]{FFFFC7}IMP-10 & 0    & 206.3333 & 2.6667 & 0   & 1.8333 & 1   & 0  & 9.5  & -48.2143 & 0      & 0  & -2547.5 & 0    \\
	\cellcolor[HTML]{9AFF99}IMP    & 0    & {\success217} & {\success4.3333} & 0   & {\success1.8333} & {\success1}   & 0  & {\success18} & X & 0 & 0  & X & 0    \\ 
	\bottomrule
	\end{tabular}
	\caption {Reporting the rank of all faulty statements obtained by appling \sfl{}, \comb{}-5 and \comb{}-10 to each version of the \chart{} project and performance evaluation of applying \ds{} to \sfl{} considering the top-5 (IMP-5) and top-10 (IMP-10) of the faulty classes}
	\label{table:performance}
\end{table*}
\normalsize

\begin{table}[h]
	\centering
	\setlength{\tabcolsep}{4pt}
	  \begin{tabular}{lrrr}
		\toprule
		Project            & \# (k = 5) & \# (k = 10) &  \% imp   \\ %\comments{& Failing Test Cases &}
		\midrule
		\lang{}            & 55 & 55 & 0 \%       \\   %\commentst{& 124   &  -}\\
		\cmath{}           & 87  & 91 & 3.77 \%     \\   %\comments{& 177   &  -}\\
		\closure{}         & 83  & 96  & 9.77 \%     \\   %\comments{& 350   &  -}\\
		\chart{}           & 22  & 24 & 7.69 \%      \\  %\comments{& 92    &  -}\\
		\jtime{}           & 21  & 27 & 3.70 \%       \\   %\comments{& 76    &  -}\\
		\mockito{}         & 24  & 27 & 7.89 \%    \\     %\comments{& 118   &  -}\\
		\bottomrule
	\end{tabular}
  \caption {Diagnosis capability if only considering the \sfl{} results for each version (no slicing applied)}
  \label{table:fs}
  \end{table}
  \normalsize

@@

\Sof{@todo}

@@

% \subsubsection{Applications}

% Ishii and Kutsuna ~\cite{li-huo-chen-zhong-feng-li-2013} proposed a
% technique involving dynamic slicing and SFL applied to MATLAB/Simulink
% models. The technique consists of iteratively
% generating tests that cause an error using satisfiability modulo
% theories (SMT) so that the slices generated are distinct from each
% other.  For slicing, their technique uses a program dependence graph
% (PDG) that express both data and control dependencies between blocks,
% so that the slice is built only on blocks that affect a specific line
% in the model - \textit{effective blocks}.  Their goal with the slicing
% was (1) to keep suspiciousness of a fault maximum if a target model
% has only one fault, and (2), to reduce the number of fault candidates
% obtained by the slicer.  For this, they utilize only failed test cases
% generated with SMT solvers ~\cite{peleska-vorobev-lapschies-2011} to
% calculate suspiciousness, as passed test cases might lower the
% suspiciousness of a fault.  The calculated suspiciousness is the
% number of times that a block belongs to the \textit{effective blocks}
% group by the number of total failed test cases.  Although their
% experiments and results showed promise with small models, the accuracy
% of the technique decreases when applied to models with multiple faults
% instead of one, as does the efficiency when exposed to large models,
% number of generated tests, sizes of sliced models and so on.

% \subsubsection{Automatic Program Repair}
% Automated repair techiniques have received considerable attention on
% the last decade and consists of three basic steps: fault localization, patch
% generation, and patch validation.  Regarding the fault localization
% step, Automated Program Repair (APR) tools can be guided by statistical
% fault localization techiniques to modify code which most likely
% contains the fault. On this section, we will briefly describe some of
% these tools.
% \Davino { Not necessarily on the paper and not necessarily on a related work section. To be revised/moved/sliced later. }

% GenProg\Fix{cite} is a state of the art tool based on genetic
% programming to repair defects in off-the-shelf C programs. GenProg's
% strategy to fault localization consists of instrumenting the program
% so that all lines visited when executing failing test cases are
% recorded and used on the genetic search algorithm. The algorithm
% involves serching for other parts of the program, considering that a
% program that contains an error in one area likely implements the
% correct behaviour elsewhere. The tool proved to be effective in
% reparing 16 programs involving 1.25 millions LOC, and efficient as the
% algorithm search space takes advantage of test case coverage
% information, reusing  existing program statements.

% Debroy and Wong\Fix{cite} presented a techinique for automatically
% fixing faults in a program combining both mutation and statistical
% fault localization. Using the Tarantula fault localizer\Fix{cite}, the
% techinique focus the top ranked statements in terms of suspiciousness
% for the mutation operations. The percentage of statements examined in
% search for the fault is based on the total number of statements of the
% program, with the 10 percent being a reasonable number on the subject
% programs studied.

% JAFF\Fix{cite} is a Java automatic repair tool based on evolutionary principles that uses fault localization for ranking the statements in the code in terms of suspiciousness level.
% Before searching for the fix, the Java program is translated into a syntax tree composed of nodes related to the top ranked statements being used on the search process.
% The tool uses a specific formula to get the number of nodes that will be used on the search based on the number of statements with the same rank of suspiciousness,
% with the range between 1 to 20 nodes being used on the cases studied.

% SemFix is based on symbolic execution, constraint solving and program synthesis applied to software automatic repair. The tool uses statistical fault localization (SFL) with Tarantula to
% obtain the rank of suspiciousness and iteratively takes the most suspicious statement that has not been tried out to be used on the search for a fix. Compared to GenProg, the presented tool
% took consideredably less time to find a fix for programs utilizing the same test suites. However, the authors mention that the choice of the SFL techinique could potentially affect the
% effectiviness of the tool, particularly with large programs.

% SPR\Fix{cite} \Davino{ Fan Long } is based on staged
% program repair with condition synthesis. SPR uses fault localization
% to identify target statements that will be transformed in search for a
% fix on the program. The search space is built with a list of
% statements ranked by suspiciousness level, where only the first 200
% ranked statements are considered. The authors observed that increasing
% the search space to the top 2000 statements would bring additional
% repairs, but with a obvious cost of searching a large space.
% \Davino { Another tool presented by the same authors is Prophet, which uses the same search space, top 200. }

% MintHint \Fix{cite} uses statistical analysis with SFL to rank
% statements by their likelihood of being faulty. Given the ranked list,
% the tool analysis the top \textit{k} statements, where \textit{k} is a
% threshold set by the user, and proceeds with the repair algorithm
% assuming the fault can be repaired by changing a single statement.

% \Davino { Another set of automatic program repair tools that doesn't use fault localization includes: CodePhage, ClearView, PAR, RSRepair, Kali, and AutoFix, among others. }

\section{Conclusions and Future Work}\label{sec:conc}

\Sof{@todo}

\section*{Acknowledgments}

\Sof{...}

@@

\begin{appendices}
	\section{Other data that might be interesting to report}
	This section has the only purpose of presenting and discussing other data that 
	are not intended yet to be used in the paper. If you find something interesting 
	in this block of information, please report.

	\begin{figure*}
		\centering
		\includegraphics[width=\textwidth]{figures/Chart_abs.pdf}
		\caption{Comparing the rank of all faulty statetments for each project version obtained by \sfl{} and \comb{} considering the top-5 and top-10 of classes}
		\begin{tabular}{r@{: }l}
			SFL & Rank of all faulty statements only using \sfl{}\\
			LS-$5$& Rank of all faulty statements after slicing the top-5 classes \\
			LS-$10$& Rank of all faulty statements after slicing the top-10 classes 
		\end{tabular}
		\label{fig:ranking}
	\end{figure*}

	\begin{figure*}
		\centering
		\includegraphics[width=\textwidth]{figures/Chart_abs_imp.pdf}
		\caption{\sfl{} rank improvement by applying \ds{} to the top-5 and top-10 classes of each project version}
		\begin{tabular}{r@{: }l}
			IMP-$5$& \sfl{} rank improvement by applying \ds{} to the top-5 classes \\
			IMP-$10$& \sfl{} rank improvement by applying \ds{} to the top-10 classes
		\end{tabular}
		\label{fig:performance}
	\end{figure*}

\end{appendices}
